### 2019-11-09 Kajian-Pustaka.tex
Fix CCG equation

\begin{small}
\begin{align*}
  {Pamungkas} &\vdash NP: \so{pamungkas}\\
  {Setyo} &\vdash NP: \so{setyo}\\
  {dan} &\vdash CONJ: \lambda x.\lambda y.\lambda f.\lambda z.\ ((f\ x)\ z) \land ((f\ y)\ z)\\
  {menyukai} &\vdash (S{\backslash}NP)/NP: \lambda x.\lambda y.\ suka(x, y)\\
  {rendang} &\vdash NP: \so{rendang}
\end{align*}
\end{small}

@@

\begin{center}
  \bgroup
  \catcode`!=\active \def!{\upshape}
  \catcode`?=\active \def?#1{\makebox[0pt]{#1}}
  \catcode`^=\active \def^#1{\footnotesize{#1}}
  \catcode`*=\active \def*#1{\scriptsize{#1}}
  \tabbedShortstack{
    !^Pamungkas & & !^dan & & !^Setyo & & !^menyukai & & !^rendang &\\
    \TABcline{1,3,5,7,9}
    !^{$NP$} & &
      !^{$CONJ$} & &
      !^{$NP$} & &
      !^{$(S\backslash NP)/NP$} & &
      !^{$NP$} &\\
    !{*: \so{pamungkas}} & &
      !{*: $\lambda x.\lambda y.\lambda f.\lambda z.\ ((f\ x)\ z) \land ((f\ y)\ z)$} & &
      !{*: \so{setyo}} & &
      !{*: $\lambda x.\lambda y.\ suka(x, y)$} & &
      !{*: \so{rendang}} &
  }
  \egroup
\end{center}

@@

\begin{center}
  \bgroup
  \catcode`!=\active \def!{\upshape}
  \catcode`?=\active \def?#1{\makebox[0pt]{#1}}
  \catcode`^=\active \def^#1{\footnotesize{#1}}
  \catcode`*=\active \def*#1{\scriptsize{#1}}
  \tabbedLongunderstack{
    !^Pamungkas & & !^dan & & !^Setyo & & !^menyukai & & !^rendang &\\
    \TABcline{1,3,5,7,9}
    !^{$NP$} & &
      !^{$CONJ$} & &
      !^{$NP$} & &
      !^{$(S\backslash NP)/NP$} & &
      !^{$NP$} &\\
    !{*: \so{pamungkas}} & &
      !{*: $\lambda x.\lambda y.\lambda f.\lambda z. ((f\ x)\ z) \land ((f\ y)\ z)$} & &
      !{*: \so{setyo}} & &
      !{*: $\lambda x.\lambda y.\ suka(x, y)$} & &
      !{*: \so{rendang}} &\\
    \TABrule & \TABrule &
      \TABrule & \TABrule &
      \TABrule\CCGCOOR & &
      & &
      &\\
    & &
      ?{^{$NP$}{*: $\lambda f. \lambda z.\ ((f\ \so{pamungkas})\ z) \land ((f\ \so{setyo})\ z)$}}
      \ \ \ \ \ \ \ 
      & & & & & & & & & &\\
    \TABrule & \TABrule &
      \TABrule & \TABrule &
      \TABrule & \TABrule &
      \TABrule\CCGFA & &
      &\\
    & &
      \ \ \ \ \ \ \ \ \ \ \ 
      ?{^{$(S\backslash NP)$}{*: $\lambda z.\ ((\lambda y.\ suka(\so{pamungkas}, y))\ z) \land
        ((\lambda y.\ suka(\so{setyo}, y)\ z))$}}
      & & & & & & & & & &\\
    \TABrule & \TABrule &
      \TABrule & \TABrule &
      \TABrule & \TABrule &
      \TABrule & \TABrule &
      \TABrule\CCGBA &\\
    & &
      \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ 
      ?{^{$S$}{*: $suka(\so{pamungkas}, \so{rendang}) \land suka(\so{setyo}, \so{rendang})$}}
      & & & & & & & & & &
  }
  \egroup
\end{center}

>>>>

\begin{small}
\begin{align*}
  {Pamungkas} &\vdash NP: \so{pamungkas}\\
  {Setyo} &\vdash NP: \so{setyo}\\
  {dan} &\vdash CONJ: \lambda x.\lambda y.\lambda f.\ (f\ x) \land (f\ y)\\
  {menyukai} &\vdash (S{\backslash}NP)/NP: \lambda x.\lambda y.\ suka(y, x)\\
  {rendang} &\vdash NP: \so{rendang}
\end{align*}
\end{small}

@@

\begin{center}
  \bgroup
  \catcode`!=\active \def!{\upshape}
  \catcode`?=\active \def?#1{\makebox[0pt]{#1}}
  \catcode`^=\active \def^#1{\footnotesize{#1}}
  \catcode`*=\active \def*#1{\scriptsize{#1}}
  \tabbedShortstack{
    !^Pamungkas & & !^dan & & !^Setyo & & !^menyukai & & !^rendang &\\
    \TABcline{1,3,5,7,9}
    !^{$NP$} & &
      !^{$CONJ$} & &
      !^{$NP$} & &
      !^{$(S\backslash NP)/NP$} & &
      !^{$NP$} &\\
    !{*: \so{pamungkas}} & &
      !{*: $\lambda x.\lambda y.\lambda f.\ (f\ x) \land (f\ y)$} & &
      !{*: \so{setyo}} & &
      !{*: $\lambda x.\lambda y.\ suka(y, x)$} & &
      !{*: \so{rendang}} &
  }
  \egroup
\end{center}

@@

\begin{center}
  \bgroup
  \catcode`!=\active \def!{\upshape}
  \catcode`?=\active \def?#1{\makebox[0pt]{#1}}
  \catcode`^=\active \def^#1{\footnotesize{#1}}
  \catcode`*=\active \def*#1{\scriptsize{#1}}
  \tabbedLongunderstack{
    !^Pamungkas & & !^dan & & !^Setyo & & !^menyukai & & !^rendang &\\
    \TABcline{1,3,5,7,9}
    !^{$NP$} & &
      !^{$CONJ$} & &
      !^{$NP$} & &
      !^{$(S\backslash NP)/NP$} & &
      !^{$NP$} &\\
    !{*: \so{pamungkas}} & &
      !{*: $\lambda x.\lambda y.\lambda f.\ (f\ x) \land (f\ y)$} & &
      !{*: \so{setyo}} & &
      !{*: $\lambda x.\lambda y.\ suka(y, x)$} & &
      !{*: \so{rendang}} &\\
    \TABrule & \TABrule &
      \TABrule & \TABrule &
      \TABrule\CCGCOOR & &
      \TABrule & \TABrule &
      \TABrule\CCGFA &\\
    & &
      ?{^{$NP$}}
      \ \ \ \ \ \ \ \ \ 
      & & & &
      \ \ \ \ \ \ \ 
      ?{^{$S\backslash NP$}}
      & & &\\
    & &
      ?{*: $\lambda f.\ (f\ \so{pamungkas}) \land (f\ \so{setyo})$}
      \ \ \ \ \ \ \ \ \ 
      & & & &
      \ \ \ \ \ \ \ 
      ?{*: $\lambda y.\ suka(y, \so{rendang})$}
      & & &\\
    \TABrule & \TABrule &
      \TABrule & \TABrule &
      \TABrule & \TABrule &
      \TABrule & \TABrule &
      \TABrule\CCGBA &\\
    & & &
      ?{^{$S$}}
      & & & & & &\\
    & & &
      ?{*: $suka(\so{pamungkas}, \so{rendang}) \land suka(\so{setyo}, \so{rendang})$}
      & & & & & &
  }
  \egroup
\end{center}
